BERT Model Compression and Weight Sharing

### 2019-05-13 paper/paper.tex
Include mention of lottery ticket paper in conclusion

% TODO: reverse of deeptwist -- what paper was this?

>>>>

\citet{frankle2018lottery} articulate in their ``lottery ticket hypothesis''
that most networks contain sparse sub-networks which can perform similarly well.
They provide an algorithm for finding these ``lottery tickets'' whose main
differences to DeepTwist are (1) that weights that get distorted to 0 are permanently
masked and kept at 0, and (2) that the algorithm progressively increases the
pruning rate. This framework could serve as a competitive alternative to
DeepTwist, and it would be interesting to see how it performs with difference
pruning.
